Different forms of uncertainty differently affect the evolution of social learning

### 2022-07-19 ms.tex
added paragraph on soc learn as a scaffold to help explain new par on pilow results

@@

???$\pilow$ paragraph???

>>>>

\subsubsection{Social learning as a scaffold for individual learning}

In this model, being a social learner is beneficial when it is more likely
on average to provide greater net payoffs than being an individual learner,
since evolution here acts as an optimization routine. 
Note that, unlike some models in the literature, it is not catastrophic for an 
individual to receive outdated information\cite[, e.g]{Rogers1988}. Instead,
agents can explore alternatives and greedily perform the observed optimal behavior
if they learned outdated information due to environmental variability. We rely
on this mechanism in the Analysis to explain patterns we observe where
social learning evolves when $u > 0.5$, meaning that the
optimal behavior will switch between generations more often than not. If 
agents could not adjust to changing conditions like this, it seems like 
social learning would not evolve when $u > 0.5$.

@@

Payoff ambiguity had a modest effect when $\pilow = 0.1$ increased to $\pilow = 0.45$,
causing social learning to be favored across more values of $u$, across all
selection set sizes and lifespans (first two rows of Figure~\ref{fig:mainResults}). 
This indicates that increased payoff ambiguity significantly increases the 
difficulty of discerning which behavior is optimal since agents evolve to 
risk social learning at greater values of $u$.
When $\pilow = 0.8$ the largest effect is smoothing and flattening of the $\meansl$ curves,
which indicates more drift (bottom row of Figure~\ref{fig:mainResults}). 
Initially this results in less frequent evolution
of social learning for the same values of $u$ and $B$. But after 
the $u$ value where $\meansl \approx 0.5$, social learning evolves more frequently than
for the same $u$ and $B$. When $\pilow \to \pihigh$, agents do better and better
whether they are social learners or not. We see that this leads to less penalty
for trying social information before possibly having to correct course due to
outdated social information.
